Applications of limited information strategies in Menger's game

### 2015-09-25 articles/applications-of-limited-information-strategies-in-mengers-game/article.tex
preprint ready to rock

\begin{abstract}
  I need an abstract
\end{abstract}

@@

I require an introduction.

@@

Recall the following definition.

@@

Recall the following definitions.

@@

A natural question arises: is there an example of a space \(X\) for which
\(\pl F\kmarkwin{2}\menGame{X}\) but \(\pl F\notmarkwin\menGame{X}\)? We quickly
see that perhaps the simplest example of a Lindel\"of non-\(\sigma\)-compact
space has this property.

@@

One may prove directly that
  \(\pl F \notmarkwin \menGame{\oneptlind{\omega_1}}\)
without much effort; however, we postpone stating this until we have
shown that being Markov Menger is equivalent to being \(\sigma\)-compact
in regular spaces.

The greatest advantage of a strategy which has knowledge of two or more previous
moves of the opponent, versus only knowledge of the most recent move, is the
ability to react to changes from one round to the next. It's this ability to
react that often allows a player to wield a winning \(2\)-Markov strategy when
a winning \(1\)-Markov strategy does not exist.

\section{Scheepers' filling games}

@@

\begin{game}
  Let \(\schFillStrictGame\kappa\) denote
  \term{Scheepers' strict union filling game}
  with two players \(\pl C\), \(\pl F\). In round \(0\), \(\pl C\) chooses
  \(C_0\in[\kappa]^{\leq\omega}\), followed by \(\pl F\) choosing
  \(F_0\in[\kappa]^{<\omega}\). In round \(n+1\), \(\pl C\) chooses
  \(C_{n+1}\in[\kappa]^{\leq\omega}\) such that \(C_{n+1}\supset C_n\), followed
  by \(\pl F\) choosing \(F_{n+1}\in[\kappa]^{<\omega}\).

@@

\begin{game}
  Let \(\schFillGame\kappa\) denote the
  \term{union filling game} which proceeds analogously
  to \(\schFillStrictGame\kappa\), except that \(\pl C\)'s restriction in round \(n+1\)
  is reduced to \(C_{n+1}\supseteq C_n\).
\end{game}

\begin{game}
  Let \(\schFillInitialGame\kappa\) denote the
  \term{initial filling game} which proceeds analogously
  to \(\schFillGame\kappa\), except that \(\pl F\) wins whenever
  \(\bigcup_{n<\omega}F_n\supseteq C_0\).
\end{game}

\begin{game}
  Let \(\schFillIntGame\kappa\) denote the
  \term{intersection filling game} which proceeds analogously
  to \(\schFillInitialGame\kappa\), except that \(\pl C\) may choose any
  \(C_n\in[\kappa]^{\leq\omega}\) each round, and \(\pl F\) wins whenever
  \(\bigcup_{n<\omega}F_n\supseteq\bigcap_{n<\omega}C_n\).
\end{game}

@@

    &
    \pl F \ktactwin{k+1}\schFillStrictGame\kappa \\
  };
  \path[>=latex,->]
    (m-1-1) edge (m-2-1)
    (m-1-2) edge (m-2-2)
    (m-3-2) edge (m-2-2);
  \path[>=latex,<->]
    (m-1-1) edge (m-1-2)
    (m-2-1) edge (m-2-2);
\end{tikzpicture}
\end{center}
\caption{Diagram of Scheepers/Menger game implications}
\label{fillingGamesDiagram}
\end{figure}

\begin{theorem}
For any cardinal \(\kappa\geq\omega\) and integer \(k<\omega\),
Figure \ref{fillingGamesDiagram} holds.
\end{theorem}

@@

While we have not shown a direct implication between the Menger game and
Scheeper's original filling game, Scheepers introduced the statement
\(\alcompS\kappa\) relating to the almost-compatability of injective functions
from countable subsets of \(\kappa\) into \(\omega\) which may be applied to
both.

@@

    &
    &
    \pl F \ktactwin2\schFillStrictGame\kappa \\
  };
  \path[>=latex,->]
    (m-2-1) edge (m-1-2)
    (m-2-1) edge (m-2-2)
    (m-2-1) edge (m-3-3)
    (m-1-2) edge (m-2-2)
    (m-1-3) edge (m-2-3)
    (m-3-3) edge (m-2-3);
  \path[>=latex,<->]
    (m-1-2) edge (m-1-3)
    (m-2-2) edge (m-2-3);
\end{tikzpicture}
\end{center}
\caption{Diagram of Filling/Menger game implications with \(\alcompS\kappa\)}
\label{fillingGamesDiagram2}
\end{figure}

\begin{theorem}
  \(\alcompS\kappa\) implies the game-theoretic results in
  Figure \ref{fillingGamesDiagram2}.
\end{theorem}

@@

Note that while it's consistent that
\(\pl F\kmarkwin2\menGame{\oneptlind{\mf c}}\), \(\oneptlind{\kappa}\)
for \(\kappa>\mf c\) is a candidate to answer the above question.

We are also interested in non-game-theoretic characterizations of these
covering properties. It has been known for some time that metrizable perfect
Menger spaces are exactly the metrizable \(\sigma\)-compact spaces, shown first
by Telgarksy in \cite{MR753073} and later directly by Scheepers in
\cite{MR1273523}. It's Scheepers' technique which gives inspiration to
the following.

@@

To help describe \(\pl F\kmarkwin2\menGame{X}\) topologically, we introduce a
slight variant of the Menger game and a related covering property.

\begin{game}
  Let \(\menGame{X,Y}\) denote the \term{Menger subspace game} which proceeds
  analogously to the Menger game, except that \(\pl F\) wins whenever
  \(\bigcup_{n<\omega} \mc F_n\) is a cover for \(Y\subseteq X\).
\end{game}

@@

\begin{theorem}
  \(\alcompS\kappa\) implies \(\oneptlind\kappa\) is
  robustly Menger, and thus
  \(\pl F\kmarkwin2\menGame{\oneptlind\kappa}\).
\end{theorem}

@@

\begin{question}
  Does there exist a space which is \(2\)-Markov Menger, but not
  robustly Menger?
\end{question}

>>>>

\begin{abstract}
  As shown by Telgarsky and Scheepers,
  winning strategies in the Menger game characterize
  \(\sigma\)-compactness amongst metrizable spaces. This is improved
  by showing that winning Markov strategies in the Menger game
  characterize \(\sigma\)-compactness amongst
  regular spaces, and that winning strategies may be improved to winning
  Markov strategies in second-countable spaces.
  An investigation of
  \(2\)-Markov strategies introduces a new topological property between
  \(\sigma\)-compact and Menger spaces.
\end{abstract}

@@

@@

@@

@@

One might wonder if a \(2\)-mark may always be improved to a \(1\)-mark
as well; this is not the case.

@@

One may prove directly that
  \(\pl F \notmarkwin \menGame{\oneptlind{\omega_1}}\)
without much effort; however, we postpone stating this until we have
shown that being Markov Menger is equivalent to being \(\sigma\)-compact
in regular spaces. Likewise, we postpone proving
  \(\pl F \kmarkwin2 \menGame{\oneptlind{\omega_1}}\)
in order to consider an equivalent set-theoretic game.

Essentially,
the greatest advantage of a strategy which has knowledge of two or more previous
moves of the opponent, versus only knowledge of the most recent move, is the
ability to react to changes from one round to the next. It's this ability to
react that often allows a player to wield a winning \(2\)-Markov strategy when
a winning \(1\)-Markov strategy does not exist.

\section{Scheepers' countable-finite games}

@@

\begin{game}
  Let \(\schFillStrictGame\kappa\) denote
  \term{Scheepers' strict countable-finite union game}
  with two players \(\pl C\), \(\pl F\). In round \(0\), \(\pl C\) chooses
  \(C_0\in[\kappa]^{\leq\omega}\), followed by \(\pl F\) choosing
  \(F_0\in[\kappa]^{<\omega}\). In round \(n+1\), \(\pl C\) chooses
  \(C_{n+1}\in[\kappa]^{\leq\omega}\) such that \(C_{n+1}\supset C_n\), followed
  by \(\pl F\) choosing \(F_{n+1}\in[\kappa]^{<\omega}\).

@@

\begin{game}
  Let \(\schFillGame\kappa\) denote the
  \term{Scheepers countable-finite union game} which proceeds analogously
  to \(\schFillStrictGame\kappa\), except that \(\pl C\)'s restriction in round \(n+1\)
  is reduced to \(C_{n+1}\supseteq C_n\).
\end{game}

\begin{game}
  Let \(\schFillInitialGame\kappa\) denote the
  \term{Scheepers countable-finite initial game} which proceeds analogously
  to \(\schFillGame\kappa\), except that \(\pl F\) wins whenever
  \(\bigcup_{n<\omega}F_n\supseteq C_0\).
\end{game}

\begin{game}
  Let \(\schFillIntGame\kappa\) denote the
  \term{Scheepers countable-finite intersection game} which proceeds analogously
  to \(\schFillInitialGame\kappa\), except that \(\pl C\) may choose any
  \(C_n\in[\kappa]^{\leq\omega}\) each round, and \(\pl F\) wins whenever
  \(\bigcup_{n<\omega}F_n\supseteq\bigcap_{n<\omega}C_n\).
\end{game}

@@

    &
    \pl F \ktactwin{k+1}\schFillStrictGame\kappa \\
  };
  \path[>=latex,->]
    (m-1-1) edge (m-2-1)
    (m-1-2) edge (m-2-2)
    (m-3-2) edge (m-2-2);
  \path[>=latex,<->]
    (m-1-1) edge (m-1-2)
    (m-2-1) edge (m-2-2);
\end{tikzpicture}
\end{center}
\caption{Diagram of Scheepers/Menger game implications}
\label{GamesDiagram}
\end{figure}

\begin{theorem}
For any cardinal \(\kappa\geq\omega\) and integer \(k<\omega\),
Figure \ref{GamesDiagram} holds.
\end{theorem}

@@

While we have not shown a direct implication between the Menger game and
Scheeper's original countable-finite game, Scheepers introduced the statement
\(\alcompS\kappa\) relating to the almost-compatability of injective functions
from countable subsets of \(\kappa\) into \(\omega\) which may be applied to
both.

@@

    &
    &
    \pl F \ktactwin2\schFillStrictGame\kappa \\
  };
  \path[>=latex,->]
    (m-2-1) edge (m-1-2)
    (m-2-1) edge (m-2-2)
    (m-2-1) edge (m-3-3)
    (m-1-2) edge (m-2-2)
    (m-1-3) edge (m-2-3)
    (m-3-3) edge (m-2-3);
  \path[>=latex,<->]
    (m-1-2) edge (m-1-3)
    (m-2-2) edge (m-2-3);
\end{tikzpicture}
\end{center}
\caption{Diagram of Scheeper/Menger game implications with \(\alcompS\kappa\)}
\label{GamesDiagram2}
\end{figure}

\begin{theorem}
  \(\alcompS\kappa\) implies the game-theoretic results in
  Figure \ref{GamesDiagram2}.
\end{theorem}

@@

We are also interested in non-game-theoretic characterizations of these
covering properties. It has been known for some time that metrizable strategic
Menger spaces are exactly the metrizable \(\sigma\)-compact spaces, shown first
by Telgarksy in \cite{MR753073} and later directly by Scheepers in
\cite{MR1273523}. It's Scheepers' technique which gives inspiration to
the following.

@@

To help instigate the topological property \(\pl F\kmarkwin2\menGame{X}\),
we introduce a
slight variant of the Menger game and a related covering property.

\begin{game}
  Let \(\menGame{X,Y}\) denote the \term{Menger subspace game} which proceeds
  analogously to the Menger game, except that \(\pl F\) wins whenever
  \(Y\subseteq\bigcup_{n<\omega} F_n\).
\end{game}

@@

\begin{theorem}
  \(\alcompS\kappa\) implies \(\oneptlind\kappa\) is
  robustly Menger.
\end{theorem}

@@

\begin{question}
  Are all \(2\)-Markov Menger spaces
  robustly Menger?
\end{question}
